\documentclass{article}

\usepackage{hyperref}
\hypersetup{
	colorlinks=true,
	linkcolor=blue,
	urlcolor=cyan,}
\usepackage{booktabs}
\usepackage{textgreek}

\input{../structure.tex} % Include the file specifying the document structure and custom commands

%----------------------------------------------------------------------------------------
%	ASSIGNMENT INFORMATION
%----------------------------------------------------------------------------------------

\title{EMG Lab 3: In Class Assignment}
\author{BIOE 385 Bioinstrumentation Laboratory} 
\date{\textit{Print a copy of this sheet and bring it to lab!}}
%----------------------------------------------------------------------------------------

\begin{document}
\large
\maketitle

\textbf{Student Name:}\hfill 	\textbf{Total Grade:\ \ \ \ /20}\vspace{0.5cm}

\textbf{Student Name:}\hfill 	\textbf{Total Grade:\ \ \ \ /20}\vspace{0.5cm}

\textbf{Student Name:}\hfill 	\textbf{Total Grade:\ \ \ \ /20}\\

\underline{Pre-Lab Assignment}\\

\textbf{Student Name:}\hfill 	\textbf{Grade:\ \ \ \ /5}\vspace{0.5cm}

\textbf{Student Name:}\hfill 	\textbf{Grade:\ \ \ \ /5}\vspace{0.5cm}

\textbf{Student Name:}\hfill 	\textbf{Grade:\ \ \ \ /5}\\

Have the Instructor or Teaching Assistant initial that you have demonstrated successful completion of each task where designated.

\section*{In-Lab Assignment}
\subsection*{Safety and Electrical Isolation}
After you make these connections, have your TA or instructor check them before you connect any electrodes to the test subject.\\TA check: \underline{\hspace{2cm}}

\subsection*{EMG Amplification}
\begin{itemize}
	\item Draw the circuit you want to build for this stage:\vspace{5cm}\\TA check: \underline{\hspace{2cm}}\\
	\item Build your circuit. Test it out using the function generator in ELVIS to be sure it is behaving as you would expect. \textit{Before trying your circuit on a test subject, have the instructor or a TA check your circuit!}\\TA check: \underline{\hspace{2cm}}
\end{itemize}

\subsection*{Signal Filtering}
Draw and build the filter you would like to have for your device. Specify your cutoff frequencies and components’ values.\vspace{6cm}\\TA check: \underline{\hspace{2cm}}\\

\subsection*{Final Amplification}
Amplify your signal (second stage) using an OP07 Op Amp to a level appropriate for detection with the NI ELVIS system.\vspace{6cm}\\TA check: \underline{\hspace{2cm}}\\

\hfill \textbf{\underline{\hspace{1cm}}/15}


\end{document}
