\documentclass{article}

\input{../structure.tex} % Include the file specifying the document structure and custom commands

%----------------------------------------------------------------------------------------
%	ASSIGNMENT INFORMATION
%----------------------------------------------------------------------------------------

\title{Project 1: Optical Immunoassay Assignment (OIA)}
\author{BIOE 385 Bioinstrumentation Laboratory} 
\date{Written Report Rubric}
%----------------------------------------------------------------------------------------

\begin{document}
\large
\maketitle

\textbf{Student Name:}\vspace{0.5cm}

\textbf{Student Name:}\hfill 	\textbf{Total Grade:\ \ \ \ \underline{\hspace{1cm}}/50}\vspace{0.5cm}

\textbf{Student Name:}\hfill\\

Executive summary (\textbf{10 points total}, more details on next page)
\begin{small}
\begin{itemize}
	\item Explanation of device goals and function \hfill \underline{\hspace{1cm}}/2
	\item Physiological relevance \hfill \underline{\hspace{1cm}}/2
	\item Brief summary of equipment/technology used \hfill \underline{\hspace{1cm}}/2
	\item Brief summary of device validation \hfill \underline{\hspace{1cm}}/2
	\item Recommendations for use and future work \hfill \underline{\hspace{1cm}}/2
\end{itemize}
\end{small}\

Description of work and technical specifications (\textbf{22 points total})
\begin{small}
\begin{itemize}
	\item Overview explanation of device \hfill \underline{\hspace{1cm}}/2
	\item Circuit diagrams for each circuit \hfill \underline{\hspace{1cm}}/4
	\item Theoretical explanation of each circuit \hfill \underline{\hspace{1cm}}/2
	\item Justification for component selection \hfill \underline{\hspace{1cm}}/2
	\item Description and examples of your LabVIEW program \hfill \underline{\hspace{1cm}}/4
	\item Description of calibration procedure \hfill \underline{\hspace{1cm}}/2
	\item Data, figures, plots demonstrating calibration and testing \hfill \underline{\hspace{1cm}}/2
	\item Metrics describing accuracy and precision of each design \hfill \underline{\hspace{1cm}}/4
\end{itemize}	
\end{small}\

Recommendation to company (\textbf{10 points total})
\begin{small}
\begin{itemize}
	\item Final recommendation of circuit design \hfill \underline{\hspace{1cm}}/2
	\item Justification (including factors such as accuracy, precision, cost, and ease of implementation) \hfill \underline{\hspace{1cm}}/4
	\item Device limitations and future improvements described \hfill \underline{\hspace{1cm}}/4
\end{itemize}	
\end{small}\

Figures (\textbf{3 points total})
\begin{small}
\begin{itemize}
	\item Appropriate resolution, brightness, and contrast \hfill \underline{\hspace{1cm}}/1
	\item Figures highlight relevant information (labeling, cropping, highlighting, captioning) \hfill \underline{\hspace{1cm}}/2
\end{itemize}
\end{small}\

Format, grammar, readability (\textbf{5 points total})
\begin{small}
\begin{itemize}
	\item Table of contents with page numbers (and appendix, if applicable) \hfill \underline{\hspace{1cm}}/1
	\item Concise sentences and accurate language \hfill \underline{\hspace{1cm}}/2
	\item Grammar, spelling, and punctuation \hfill \underline{\hspace{1cm}}/2
\end{itemize}
\end{small}\
\pagebreak

\section*{Description of Executive Summary}
As a part of your technical reports, you will write an executive summary. The purpose of an executive summary is to summarize your project’s status and orient your audience to the aims, methods, and implications of your project. \textit{It should be less than one page.}\\

Organize your summary to answer the following questions:
\begin{itemize}
	\item What problem are you trying to solve?
	\item Why is solving this problem interesting or important?
	\item How will/does your design solve the problem?
	\begin{itemize}
		\item How will/does it work and why did you choose this specific approach over other options?
	\end{itemize}
	\item How will/did you validate your design?
	\begin{itemize}
		\item What surprises, new discoveries, or anomalies have/did you encounter?
		\item What do your performance results suggest about the solution you proposed?
	\end{itemize}
	\item Which device would you recommend to use for the final design and why?
	\begin{itemize}
		\item What recommendations do you have for improving or building on your design?
		\item What do you plan to do next or what recommendations can you make to others that might conduct follow-up studies?
	\end{itemize}
\end{itemize}\

In some cases, \textbf{the executive summary might be all that your boss or a decision-maker reads} when evaluating your project and determining a course of action, so it is important to be concise, yet thorough.

\end{document}
